Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Better tables
Reviewing Methodology pt. IV, rewriting a bit and mostly killing parenthesis and 'moreovers'

Once a dataset has been composed it must be preprocessed, i.e. it
should be revised in order to fix the existing errors (such as wrong
or duplicated patterns), or to complete (or address) the absence of
information, for instance. The aim is looking for the correctness,
homogeneity and completeness of the data. % useless paragraph - JJ

@@

After this, the features describing every pattern are frequently analysed.
In this case, among the variables describing a new book, some may affect 
predictions (those variables provide information), while others may not be 
necessary and even redundant.

% You have to justify its application to this particular problem. What
% was the runnning time with all variables? What reduction was your
% target? - JJ
Moreover, the algorithm running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature reduction is a task that is usually
applied in these kind of situations, having two ways of performance
\cite{kittler1986feature}: feature extraction and feature selection.  
% two ways of performance? WTF? Do you mean "being performed in two
% different ways?" - JJ
%Feature selection task is usually carried out by 
%searching through all possible combinations of features, evaluating each one.

>>>>

Preprocessing a dataset means that it is revised in order to reduce errors, such as wrong or duplicated patterns, or for completing missing values. The aim is to look for the correctness,
homogeneity, and completeness of the data. % useless paragraph - JJ

@@

After this process, the features describing every pattern are frequently analysed.
In this case, among the variables describing a new book, some may affect 
predictions as they provide information, while others may not be 
necessary and even redundant.

% You have to justify its application to this particular problem. What
% was the runnning time with all variables? What reduction was your
% target? - JJ
Additionally, the algorithm running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature reduction is a task that is usually
applied in these kind of situations, having two ways of performance
\cite{kittler1986feature}: feature extraction and feature selection.  
% two ways of performance? WTF? Do you mean "being performed in two
% different ways?" - JJ
%Feature selection task is usually carried out by 
%searching through all possible combinations of features, evaluating each one.
